\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-10-30 analysis/paper/paper.Rmd
methods text

Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)

The code to do this is provided in the research compendium here:[https://github.com/vscholl/neonHScompendium](https://github.com/vscholl/neonHScompendium).

>>>>

**Filtered plants to keep only "live" ones**
**Mask created for water absorption bands (cite)**

We provide all of our code in a research compendium here:[https://github.com/vscholl/neonHScompendium](https://github.com/vscholl/neonHScompendium).
